Tabular Constraint Learning

### 2016-04-14 Paper/ECAI/tabular.tex
Removed comments and corrected lookup

\sergey{Table should take into account our new notation and balance between formality and intuition, heh}
\begin{table*}
  \centering
  \begin{tabularx}{\textwidth}{l X X}
    \textbf{\CName} & \textbf{\CSignature} & \textbf{\CFunction}\\
    \ecalldiff{v_x} & $\integer(v_x)$ or $\textual(v_x)$ & All elements in $v_x$ are different \\
    %X = Y & & \\
    \ecfkey{v_{fk}}{v_{pk}} & $\ptype(v_{fk})$ = $ptype(v_{pk})$,$\ptable(v_{fk}) \neq \ptable(v_{pk})$, $\ecalldiff{v_{pk}}$ & Every value in @fk also exist in @pk \\
    % TODO check out
    \eclookupprod{v_r}{v_1}{v_{fk}}{v_{pk}}{v_{val}}
      & the variables in $\{@r, @1, @fk\}$ and in $\{@pk, @val\}$ all have the same \plength, \ptable and \por.
      & $@r$ is the obtained by multiplying $@1$ with $\eclookup{@fk}{@pk}{@val}$  
      \\
    \eclookup{v_r}{v_{fk}}{v_{pk}}{v_{val}}
      & the variables in $\{@fk, @val\}$ and in $\{@pk, @r\}$ all have the same \plength, \ptable and \por; $@r$ and~$@val$ have the same type; and \ecfkey{@fk}{@pk}.
      & Lookup $@fk$ in $@pk$ and return the corresponding value in $@val$.
      \\
    \eclookupfuzzy{v_r}{v_{fk}}{v_{pk}}{v_{val}} & & \\
    \ecperm{v_x} & & \\
    \ecprod{v_r}{v_1}{v_2} & & \\
    \ecproj{v_r}{\mathbf{v_x}} & & \\
    \ecrank{v_r}{v_x} & Y and X have the same length & Y is the rank of X (including ties)\\
    \ectotal{v_r}{v_{pos}}{v_{neg}} & A, P and N have the same length and their length is at least 2 & *\\
    \ecseries{v_x} & & \\
    \ecsumc{v_r}{\mathbf{v_x}} & & Y is the result of summing each column in X \\
    \ecsumr{v_r}{\mathbf{v_x}} & & Y is the result of summing each row in X \\
    \ecsumif{v_r}{v_{fk}}{v_{pk}}{v_{val}} & & \\
    \ecsumprod{v_r}{v_1}{v_2} & & \\

@@

\subsubsection{Results}
\sergey{Samuel, you should just say at the beginning that all experiments has been run on macbook la-la system and that's it, I guess, I don't think we need to mention it multiple times}
Our current implementation takes a few seconds to find 18 constraints, including all of the 12 solutions described in Figure~\ref{fig:sol_example}.
Of the 6 remaining (redundant) constraints, 5 are $\mathit{rank}$ constraints that are true by accident, such as: \begin{align*}
  & \ecrank{\range{T_1}{\rangeall}{1}}{\range{T_1}{\rangeall}{5}}
\end{align*}
The other redundant constraint is an additional $\mathit{lookup}$ that holds because the two vectors in \range{T_2}{\rangeall}{\rangeto{2}{3}} can both be used to look each other up in \range{T_1}{\rangeall}{\rangeto{1}{2}} and we considered only one of them to be essential (lookup using the ID).

@@

\subsubsection*{Q1. How accurate is the approach?}
\sergey{that's confusing, it can do 100\% but then all of a sudden 96\%, short explanation needed}
Fortunately, our system is currently able to find $100\%$ of the implemented constraints (90) on the benchmark suite.
There are only three essential constraints that have not been implemented yet, therefore our system currently identifies $96.77\%$ of the essential constraints.

>>>>

\sergey{Table should take into account our new notation and balance between formality and intuition, heh}
\begin{table*}
  \centering
  \begin{tabularx}{\textwidth}{l X X}
    \textbf{\CName} & \textbf{\CSignature} & \textbf{\CFunction}\\
    \ecalldiff{v_x} & $\integer(v_x)$ or $\textual(v_x)$ & All elements in $v_x$ are different \\
    %X = Y & & \\
    \ecfkey{v_{fk}}{v_{pk}} & $\ptype(v_{fk})$ = $ptype(v_{pk})$,$\ptable(v_{fk}) \neq \ptable(v_{pk})$, $\ecalldiff{v_{pk}}$ & Every value in @fk also exist in @pk \\
    % TODO check out
    \eclookupprod{v_r}{v_1}{v_{fk}}{v_{pk}}{v_{val}}
      & the variables in $\{@r, @1, @fk\}$ and in $\{@pk, @val\}$ all have the same \plength, \ptable and \por.
      & $@r$ is the obtained by multiplying $@1$ with $\eclookup{@fk}{@pk}{@val}$  
      \\
    \eclookup{v_r}{v_{fk}}{v_{pk}}{v_{val}}
      & the variables in $\{@fk, @r\}$ and in $\{@pk, @val\}$ all have the same \plength, \ptable and \por; $@r$ and~$@val$ have the same type; and \ecfkey{@fk}{@pk}.
      & Lookup $@fk$ in $@pk$ and return the corresponding value in $@val$.
      \\
    \eclookupfuzzy{v_r}{v_{fk}}{v_{pk}}{v_{val}} & & \\
    \ecperm{v_x} & & \\
    \ecprod{v_r}{v_1}{v_2} & & \\
    \ecproj{v_r}{\mathbf{v_x}} & & \\
    \ecrank{v_r}{v_x} & Y and X have the same length & Y is the rank of X (including ties)\\
    \ectotal{v_r}{v_{pos}}{v_{neg}} & A, P and N have the same length and their length is at least 2 & *\\
    \ecseries{v_x} & & \\
    \ecsumc{v_r}{\mathbf{v_x}} & & Y is the result of summing each column in X \\
    \ecsumr{v_r}{\mathbf{v_x}} & & Y is the result of summing each row in X \\
    \ecsumif{v_r}{v_{fk}}{v_{pk}}{v_{val}} & & \\
    \ecsumprod{v_r}{v_1}{v_2} & & \\

@@

\subsubsection{Results}
Our current implementation takes a few seconds to find 18 constraints, including all of the 12 solutions described in Figure~\ref{fig:sol_example}.
Of the 6 remaining (redundant) constraints, 5 are $\mathit{rank}$ constraints that are true by accident, such as: \begin{align*}
  & \ecrank{\range{T_1}{\rangeall}{1}}{\range{T_1}{\rangeall}{5}}
\end{align*}
The other redundant constraint is an additional $\mathit{lookup}$ that holds because the two vectors in \range{T_2}{\rangeall}{\rangeto{2}{3}} can both be used to look each other up in \range{T_1}{\rangeall}{\rangeto{1}{2}} and we considered only one of them to be essential (lookup using the ID).

@@

\subsubsection*{Q1. How accurate is the approach?}
Fortunately, our system is currently able to find $100\%$ of the implemented constraints (90) on the benchmark suite.
There are only three essential constraints that have not been implemented yet, therefore our system currently identifies $96.77\%$ of the essential constraints.
